CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2019-03-22 gpus/paper.tex
more intro work

@@

With GPU accelerators becoming increasingly dominant, algorithms need to be ported.
There are a number of descriptions of GPU-enabled astrophysical hydro codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018,wang:2010} \MarginPar{todo: group by AMR/no-AMR, GPU exclusive, Kokkos, ...}

In this paper, we describe our approach to performance portability.
Our goal is to have the same computational kernels run efficiently on
CPUs (including manycore processors) and GPUs.  We describe the work
we needed to do to enable this portability and show performance
metrics for a reacting flow problem in astrophysics.

\section{The Castro hydrodynamics code}

>>>>

Supercomputer architectures have evolved a lot over the past
decades~\citep{bell:2015}.  Shared memory vector machines with custom
processors dominated early, displaced in the early 1990s by
distributed memory, massively parallel architectures built upon
commodity CPUs where the message passing interface (MPI) became the
dominant library for achieving parallelism.  As core counts increased,
threading because increasingly important, and OpenMP became the
standard for threading in high-performance computing, with hybrid
MPI+OpenMP approaches to parallelism.  In the race to increase
performance while keeping electrical power consumption reasonable,
accelerators were increasingly turned to, include GPUs and many-core
chips like the Intel Phi series.  The simulation codes we use in
astrophysics need to keep pace with these developments, or they will
not be able to run on the next generation of supercomputers.  In
particular, GPUs are dominant now, so existing algorithms need to be
ported to run on GPUs, or new codes need to be written from scratch
targeting the new architecture.

There are a number of descriptions of GPU-enabled astrophysical hydro
codes, including
\citet{gamer,cholla,fargo3d,pekkila:2017,caplan:2018,racz:2018,liska:2018,goz:2018,wang:2010} \MarginPar{todo:
  group by AMR/no-AMR, GPU exclusive, Kokkos, ...}

In this paper, we describe our approach to performance portability
with the \castro\ multiphysics simulation code..  Our goal is to have
the same computational kernels run efficiently on CPUs (including
manycore processors) and GPUs.  We describe the work we needed to do
to enable this portability and show performance metrics for a reacting
flow problem in astrophysics.

\subsection{The Castro hydrodynamics code}

@@
